Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2021-05-10 Scripts/Initial_Analysis.Rmd
Cleaned script

  spp <- bind_rows(
    lapply(Taxon_list,SummaryProp,links)
  ) %>% 
    spread(time_step,mean_spp) %>% 
    # mutate_if(is.numeric,replace_na,0) %>% # If NA 0 meaning wins and looses
    mutate_at(vars(
      "per_early" = early,
      "per_mid" = mid
    ),
    funs(round(((.-historical)/(abs(historical)))*100,2))) %>%  # original
         # funs(round(((historical-.)/(abs((historical+.)/2)))*100,2)
    # funs((historical-.)*100)) %>%  
    # funs(ifelse(variable == "n_per",.,round(((.-historical)/(abs(historical)))*100,2)
                # )
         # )
    # ) %>%
  gather("time_step","percentage_change",per_early:per_mid)

@@

  proportion_change <- eez %>% 
    gather("variable","value",n_spp:n_per) %>% 
    spread(time_step,value) %>% 
    mutate_at(vars(
      "per_early" = early,
      "per_mid" = mid
    ),
    # funs(round(((.-historical)/(abs(historical)))*100,2)
    funs(ifelse(variable == "n_per",.,round(((.-historical)/(abs(historical)))*100,2) # original
    #             )
    # funs(ifelse(variable == "n_per",.,(historical-.)*100)
                )
         )
    )

>>>>

  spp <- bind_rows(
    lapply(Taxon_list,SummaryProp,links)
  ) %>% 
    spread(time_step,mean_spp) %>% 
    # mutate_if(is.numeric,replace_na,0) %>% # If NA 0 meaning wins and looses
    mutate_at(vars(
      "per_early" = early,
      "per_mid" = mid
    ),
    funs(round(((.-historical)/(abs(historical)))*100,2))
    ) %>%  # original
  gather("time_step","percentage_change",per_early:per_mid)

@@

  proportion_change <- eez %>% 
    gather("variable","value",n_spp:n_per) %>% 
    spread(time_step,value) %>% 
    mutate_at(vars(
      "per_early" = early,
      "per_mid" = mid
    ),
    funs(ifelse(variable == "n_per",.,round(((.-historical)/(abs(historical)))*100,2) # original
                )
         )
    )
